Identifying Software Performance Changes Across Variants and Versions

### 2020-08-11 paper.tex
added CCS concepts to tex file

@@

	%%
	%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
	%% Please copy and paste the code instead of the example below.h
	%%
	%% Keywords. The author(s) should pick words that accurately describe
	%% the work being presented. Separate the keywords with commas.
	\keywords{software performance, software evolution, configurable software systems, machine learning, reinforcement learning}

>>>>

	\begin{CCSXML}
		<ccs2012>
		<concept>
		<concept_id>10011007.10010940.10011003.10011002</concept_id>
		<concept_desc>Software and its engineering~Software performance</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		<concept>
		<concept_id>10010147.10010257.10010282.10011304</concept_id>
		<concept_desc>Computing methodologies~Active learning settings</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		<concept>
		<concept_id>10011007.10011074.10011111.10011113</concept_id>
		<concept_desc>Software and its engineering~Software evolution</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		</ccs2012>
	\end{CCSXML}

	\ccsdesc[500]{Software and its engineering~Software performance}
	\ccsdesc[500]{Computing methodologies~Active learning settings}
	\ccsdesc[500]{Software and its engineering~Software evolution}

@@

	%%
	%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
	%% Please copy and paste the code instead of the example below.h
	%%
	%% Keywords. The author(s) should pick words that accurately describe
	%% the work being presented. Separate the keywords with commas.
	\keywords{software performance, software evolution, configurable software systems, machine learning, active learning}
